---
title: "iCourse Investigation"
author: "Will Morgan"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      fig.dim = c(7,3.5))

libs <- c('readxl', 'tidyverse', 'data.table', 'gridExtra', 'stringr', 'magrittr')
lapply(libs, library, character.only = TRUE)

# Use local data if available
if (file.exists("Data/full_data.csv")) {
  data <- suppressWarnings(fread("Data/full_data.csv"))
} else {
  data <- suppressWarnings(fread(paste0(ps, "full_data.csv")))
}
```


## Purpose and Outline

This is an exploratory investigation into the characteristics of iCourses and is
meant to be a log of the questions that arise as we delve further into the data.
For now we focus on answering only a handful of questions we think will be informative
down the line when we begin looking into student course selection. The current
list of questions is as follows:

1. How many and what types of courses exist in both modalities?

2. What is the proportion of face-to-face (F2F) courses that have iCourse (ICO)
equivalents?
    
    + How does this change when we disaggregate by college? program?

3. What proportion of iCourses are upper-division?
  
4. What proportion of on-campus students' courses are taken as iCourses?
  
    + Does this vary w.r.t. other variables of interest? (GPA, college, etc.)
    
5. Is there a relationship between iCourse enrollment and the amount of credits a 
student is taking?

6. What proportion of iCourses are being taken to fulfill core degree requirements?

\pagebreak

## Question 1: Course Equivalencies

The first objective will simply be to investigate the number and types of courses
that exist in both modalities. Before quantifying anything, we eliminate observations
occurring before the Summer 2011 term as the `iCourse` modality was not fully in 
place before that time. Any observations occurring in the Winter 2014 term are also
dropped because only Face-to-Face courses were offered in that term. Lastly,
we drop anybody that is not an undergraduate student.

```{r q1 subset}
data %<>%
  filter(crse_modality %in% c("F2F", "ICOURSE"),
         stud_modality == "F2F",
         strm >= 2114 & strm != 2149,
         catalog_nbr <= 499,
         acad_career == "UGRD")
  
ico_courses <- data %>%
  filter(crse_modality == "ICOURSE") %>%
  select(course) %>%
  unlist() %>%
  unique

course_list <- data %>%
  filter(crse_modality == "F2F") %>%
  select(course) %>%
  unlist() %>%
  unique() %>%
  intersect(., ico_courses)

# Prep df for some basic graphics
equivalencies <- data.frame(course = course_list, stringsAsFactors = FALSE) %>%
  mutate(subject = str_sub(course, 1, 3),
         catalog_nbr = as.numeric(str_sub(course, 5, 7)))
```

```{r q1 graphics}
equivalencies %>%
  ggplot(aes(catalog_nbr)) +
  geom_histogram(bins = 100, fill = 'grey', color = 'black') + 
  labs(x = "Catalog Number",
       title = "F2F/ICO Equivalencies by Catalog Number") + 
  theme(plot.title = element_text(hjust = 0.5))
ggsave("Graphics/F2F_ICO equivalencies by cat_num.png")
```

Takeaways:

* More upper division than lower division

* Lower division courses appear to be mostly 101, 102, 201, 202 courses

* Most commonly occurring upper division catalog numbers seems to be numbers that
are usually reserved for topic courses (394, 398, 494, 498)

```{r}
equivalencies %>%
  group_by(subject) %>%
  summarise(count = n()) %>%
  top_n(25, count) %>%
  ggplot(aes(reorder(subject, -count), count)) + 
  geom_bar(stat = 'identity', fill = 'grey', color = 'black') +
  labs(x = "Subject",
       y = "Count",
       title = "Top 25 Occurring Subjects") + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 60, hjust = 1))
ggsave("Graphics/top 25 subj equivalencies.png")
```

Takeaways:

* English, History, and Political Science have a significant number of unique
courses that are offered


***

## Question 2: Unique Course Counts

Here we want some basic stats on the amount of courses each modality offers and
the amount of cross-over there is between each modality (how many courses exist in both,
how many are unique to a given modality). Obviously we should expect there to be 
a relatively high number of courses that are only in F2F - what will be interesting
is the amount of iCourses that do not have a F2F equivalent.

```{r}
# Number of unique F2F courses
numF2F <- length(unique(data[data$crse_modality == "F2F", "course"]))
cat("Number of unique F2F courses:", numF2F, "\n")

# Number of unique ICO
numICO <- length(unique(data[data$crse_modality == "ICOURSE", "course"]))
cat("Number of unique iCourses:", numICO, "\n")

# Number of equivalencies
cat("Number of courses that exist as ICO and F2F:", length(course_list))
# Prop of ICO equivalents
propF2F <- length(course_list) / numF2F
cat("Proportion of F2F courses with ICO equivalents:", round(propF2F, 4), "\n")

# Prop of ICO courses that have F2F equal
propICO <- 1 -length(setdiff(ico_courses, course_list)) / length(ico_courses)
cat("Proportion of iCourses with an F2F equivalent:", round(propICO, 4), "\n")
```


Approximately a quarter of F2F courses are also offerred as iCourses, and about 
one-fifth of iCourses do not have a F2F equivalent. This is higher than what I was 
expecting, so let's quickly investigate how populated these courses are:

```{r}
nonF2F <-  setdiff(ico_courses, course_list)

data %>%
  filter(course %in% nonF2F) %>%
  group_by(course) %>%
  summarise(ovall_enrl = n()) %>%
  top_n(10, ovall_enrl) %>%
  ggplot(aes(reorder(course, -ovall_enrl), ovall_enrl)) +
  geom_bar(stat = 'identity', fill = 'grey', color = 'black') +
  labs(y = "Overall Students Enrolled",
       title = "Most Enrolled iCourses w/o F2F Equal") + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank())
ggsave("Graphics/most_enrolled ico w_no f2f.png")



```


This isn't terribly exciting, but it is interesting to see that these courses
are mostly from different departments, save for MUS|362 and MUS|347. For now we
won't do anything with this info but it is good to have available.

Getting back to the question at hand, let's now investigate the proportion of
F2F-ICO equivalents by college. We aren't necessarily looking for any particular
bit of information from this but at least we can get a sense of who is making the
most use of iCourses.

_Important note:_
The original data we have been working with so far does not contain the correct
course ownership information, so we need to bring another data source. From this data
we'll use the `acad_org` (College) and `acad_group` (School) variables to do
the disaggregation


_Second Important Note:_
At the time of writing this there is no clear way to assign ownership of courses
to colleges (apparently this is much harder to suss out than I had expected). 
Since this is not a huge interest and it can still be approached in alternative 
ways (via `subject`), we'll leave this alone for now.


```{r, eval = FALSE}
ownership <- fread("Data/course_ownership.csv") %>%
  rename_all(str_to_lower) %>%
  mutate(catalog_nbr = as.numeric(str_sub(catalog_nbr, 1, 3)),
         course = paste(subject, catalog_nbr, sep = "|")) %>%
  rename(college = acad_group_descr,
         department = acad_org_descr) %>%
  select(course, college, department) %>%
  filter(!str_detect(department, "INACTIVE"))
  # group_by(course) %>%
  # slice(1) %>%
  # ungroup()


equivalencies %<>%
  left_join(., ownership, by = 'course')
```

***

## Question 3: Upper Division vs. Lower Division iCourses

This will be similar to the first question we answered, except now
we will be looking at the ~1900 iCourses and no F2F courses. First up is a quick
histogram of the catalog numbers for the 1900 iCourses in our sample.

```{r}
icourses <- data.frame(course = ico_courses, stringsAsFactors = F) %>%
  mutate(subject = str_sub(course, 1, 3),
         catalog_nbr = as.numeric(str_sub(course, 5, 7)),
         upper_division = as.factor(if_else(catalog_nbr >= 300, "UD", "LD")))

# Histogram of catalog numbers
icourses %>%
  ggplot(aes(catalog_nbr)) +
  geom_histogram(bins = 75, fill = 'grey', color = 'black') +
  labs(x = "Catalog Number",
       y = "Count",
       title = "Catalog Number Distribution") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave("Graphics/ICO cat_num hist.png")
```

We're not necessarily interested in specific numbers but rather just a vague
sense of where most of the data lies. Clearly, most of the available iCourses
are upper division courses. 

Now onto the empirical CDF:

```{r}
# ECDF of catalog numbers
icourses %>%
  ggplot() +
  stat_ecdf(aes(catalog_nbr), pad = FALSE) +
  geom_vline(xintercept = 300, linetype = "dotdash", color = 'blue') +
  labs(x = "Catalog Number",
       y = "Cumulative Density",
       title = "Cumulative Density of ICO Catalog Numbers") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave("Graphics/ICO cat_num ecdf.png")
```

The ECDF displays this idea a bit more succinctly - the dashed line separates our
sample into lower-division (to the left) and upper-division (right). Only a quarter
of all iCourses are lower-division, so we have a decently left-skewed distribution.

A small note on this - there appears to be two courses with catalog numbers less 
than 100. These are likely two week-long "Welcome to ASU" sort of courses or some
other form of irregular course type. We'll get rid of them now in case they become a
problem later. 

***

## Question 4: Proportion of Courses taken as iCourses

This will be a very general estimate of how often on-ground students are taking 
iCourses. Once we have that down, we can disaggregate by college (`acad_prog`) to
see which colleges' students are taking the most iCourses. If this doesn't reveal
much, we can easily take it a step further and split this up by degree program. 
However, since the number of degree programs is so great it will probably be best
to just look at the extremes.


```{r}
# Ov'all proportion count
data %>%
  filter(stud_modality == "F2F") %>%
  group_by(crse_modality) %>%
  summarise(modality_enrl = n()) %>%
  ungroup() %>%
  mutate(tot_enrl = sum(modality_enrl),
         prop_enrl = modality_enrl / tot_enrl) %>%
  select(crse_modality, prop_enrl) %>%
  ggplot(aes(crse_modality, prop_enrl)) +
  geom_bar(stat = 'identity', fill = 'grey', color = 'black') +
  geom_text(aes(label = round(prop_enrl, 4)), vjust = -1) + 
  ylim(0, 1) +
  labs(title = "Proportion of Enrollments by Modality") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title = element_blank())
ggsave("Graphics/prop_enrlmt by modality.png")
```

Not terribly surprising - three-quarters of the enrollments are taken in-person.
In fact, its a bit lower than I was expecting. Hopefully the disaggregation by college
will give us more information.

Just to be clear - we will be using the college associated with the students' 
degree to make these calculations, not the college to which a course belongs. In 
other words, a correct interpretation of this disaggregation might be:

"12% of all enrollments for _students_ in the College of Public Service & Community
Solutions were iCourses"

An incorrect interpretation would be:

"12% of all enrollments for _courses_ in the College of Public Service & Community
Solutions were iCourses"

Finally, when we do the disaggregation we eliminate college codes that don't correspond
to a single college. This includes codes for non-degree students, students
from the Provost's Office, and students at Thunderbird School of Global Management.

```{r}
# Proportion by College
ico_enrl_props <- data %>%
  group_by(crse_modality, acad_prog) %>%
  summarise(modality_enrl = n()) %>%
  group_by(acad_prog) %>%
  mutate(tot_enrl = sum(modality_enrl),
         prop_enrl = modality_enrl / tot_enrl) %>%
  filter(crse_modality == "ICOURSE",
         !acad_prog %in% c("UGNFA", "UGPR", "UGTB", "UGUC")) %>%
  select(crse_modality, acad_prog, prop_enrl) %>%
  ungroup()

ico_enrl_props %>%
  ggplot(aes(reorder(acad_prog, -prop_enrl), prop_enrl)) + 
  geom_bar(stat = 'identity', color = 'black', fill = 'grey') +
  geom_text(aes(label = round(prop_enrl, 3)), vjust = -1, size = 3.5) +
  labs(x = "College",
       title = "Proportion of ICO enrollments by College") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1)) +
  ylim(0, 1)
```


Top 3:

* College of Public Service & Community Solutions (UGPP), 39.5%

* College of Integrative Science & Arts (UGLS), 36.6%

* Cronkite School of Journalism & Mass Communication (UGCS), 32.1%

Bottom 3:

* Ira A. Fulton School of Engineering (UGES), 8.9%

* School for the Future of Innovation in Society (UGFI), 18.7%

* Herberger Institute (UGHI), 18.8%

We now go one step further and look at the actual degree programs that have the
highest and lowest proportions of iCourse enrollments

```{r}
# Proportion by Degree
ico_props_degree <- data %>%
  filter(acad_plan_type != c("NDG")) %>%
  group_by(crse_modality, acad_plan) %>%
  summarise(modality_enrl = n()) %>%
  group_by(acad_plan) %>%
  mutate(tot_enrl = sum(modality_enrl),
         prop_enrl = modality_enrl / tot_enrl) %>%
  filter(crse_modality == "ICOURSE",
         tot_enrl >= 1000) %>%
  select(acad_plan, prop_enrl, tot_enrl, modality_enrl) %>%
  ungroup()

ico_props_degree %>%
  top_n(10, prop_enrl) %>%
  ggplot(aes(reorder(acad_plan, -prop_enrl), prop_enrl)) + 
  geom_bar(stat = 'identity', color = 'black', fill = 'grey') +
  geom_text(aes(label = round(prop_enrl, 3)), vjust = -1, size = 3) +
  labs(x = "Degree",
       title = "Top ICO enrollments by Degree") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1)) +
  ylim(0,1)
ggsave("Graphics/top_ico_enrl by deg.png")
```
Top 5 by degree:

* Technical Communications BS (LSTECBS), 77%

* Liberal Studies BA (LABLSBLS), 65.4%

* Applied Science/Operations Management (TSIMCOBAS), 63.1%

* Applied Science BAS (ASBASBAS), 62.3%

* Health Sciences/Health Policy (NUHSCHPBS), 60.5%

```{r}

ico_props_degree %>%
  top_n(10, -prop_enrl) %>%
  ggplot(aes(reorder(acad_plan, -prop_enrl), prop_enrl)) + 
  geom_bar(stat = 'identity', color = 'black', fill = 'grey') +
  geom_text(aes(label = round(prop_enrl, 3)), vjust = -1, size = 3) +
  labs(x = "Degree",
       title = "Bottom ICO enrollments by Degree") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1)) +
  ylim(0,0.1)
ggsave("Graphics/bttm_ico_enrl by deg.png")


```

Bottom 5:

* Civil Engineering (ESCEECBSE), 4.8%

* Construction Management/Heavy Construction (ESCONHBS), 5%

* Manufacturing Engineering Technology (TSMETMBS), 5.6%

* Construction Engineering (ESCONBSE), 5.8%

* Mechanical Engineering (ESMAEMBSE), 6.1%

***

## Question 5: iCourse enrollment and Course Load

The final bit we will investigate is how iCourse enrollment proportions vary
by course load. In particular, we want to see if there is any visual difference
between the number of full-time students taking iCourses versus part-time students.

To be extremely clear, we calculate two data points for each student in a given term: the amount of units they are enrolled in, and the proportion of courses that are iCourses. Additionally, we drop the summer terms from this plot because of the reduced 
amount of credits that are taken during this term.

Also, we are aware that there are a variety of definitions for determining part-time status (some a bit less obscure than others) but for the sake of simplicity we use a very basic rule for this determination. If you are taking less than 12 credits in a particular term, you are considered to be a part-time student.

```{r}
course_load_enrl <- data %>%
  filter(term != "Summer") %>%
  mutate(ico = if_else(crse_modality == "ICOURSE", 1, 0)) %>%
  group_by(emplid, strm) %>%
  summarise(course_load = sum(unt_taken),
            prop_ico = mean(ico)) %>%
  ungroup() %>%
  filter(between(course_load, 1, 21)) %>%
  mutate(cl_type = if_else(course_load < 12, "Part-time", "Full-time"))

course_load_enrl %>%
  ggplot(aes(prop_ico, fill = cl_type, color = cl_type)) +
  geom_density(position = 'stack') +
  labs(x = "Proportion taken as ICO",
       title = "Density estimate for proportion of iCourse enrollments") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(),
        legend.title = element_blank())
ggsave("Graphics/course_load density.png")
```

Based on the density estimate plot alone, we can see that full-time students are taking fewer iCourses as a proportion of their term schedule. Part-time students on the other hand are interestingly clumping up on both extremes, with small peaks around 0.33, 0.5, and 0.66. These small peaks are likely an artefact of courses being worth on average 3 credits and the fact that we are considering part-time students to be taking less than 12 credits.

It is not exactly clear how different these distributions are or if we can even say that they are different. Before getting into any testing, let's look at the empirical CDF to understand them a little more: 

```{r}
course_load_enrl %>%
  ggplot(aes(prop_ico, color = cl_type)) + 
  stat_ecdf(pad = FALSE) +
  labs(x = "Proportion taken as ICO",
       title = "ECDF of proportion of ICO Enrollments") + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(),
        legend.title = element_blank())
ggsave("Graphics/course_load ecdf.png")
```

Alright! Now we have something interesting to work with - both of these distributions
definitely appear to be different. Let's follow up with a couple tests to determine
if we have enough evidence to say that part-time students take more or less iCourses (as a proportion of their entire term schedule)
than full time students.

We'll first use the KS test to determine if these two distributions are significantly
different. More specifically, we want to test if the distribution of the proportion
of iCourses taken in a term (`prop_ico`) is independent of full-time status.

```{r}
# Grab vectors of PT and FT Proportions
ind <- course_load_enrl$cl_type == "Full-time"

ft <- course_load_enrl[ind == TRUE, "prop_ico"] %>% unlist()
pt <- course_load_enrl[ind == FALSE, "prop_ico"] %>% unlist()

ks.test(ft, pt)
```

Great - we have more than enough evidence to say that `prop_ico` is NOT independent
of full time status. Let's get slightly more specific - now that we know that
the distribution of `prop_ico` varies with full-time status, let's test to see 
if there is any significant difference in the conditional sample means.

```{r}
ft_mean <- mean(ft)
pt_mean <- mean(pt)
ovall_mean <- mean(course_load_enrl$prop_ico)

# Test for difference in proportions
t <- (ft_mean - pt_mean) / sqrt(ovall_mean*(1-ovall_mean)*((1/length(ft)) + (1/length(pt))))

cat("Test Statistic for difference in proportions:", t, "\n")
cat("Part-time students take", round((pt_mean-ft_mean)*100, 1), "% more iCourses as a proportion of their schedule each term")

```


***

## Question 6: iCourses fulfilling degree requirements

Our final question and perhaps the most interesting one. When it comes to degree
requirements, do students view iCourses as an acceptable substitute for in-person
courses? Or are students mostly taking iCourses to fulfill more general elective
credits? The answer will be important when we start modeling a student's likelihood
of taking an iCourse. First, let's calculate the percentage of iCourses that fulfill
a core degree requirement in our sample:

```{r}
p_req <- data %>%
  filter(crse_modality == "ICOURSE",
         stud_modality == "F2F") %>%
  summarise(required_course = mean(required_course)) %>%
  unlist() %>%
  round(., 3)*100

cat(p_req, "% of all iCourses taken fulfill a core degree requirement")

```

This is a start, but it will be a little more revealing to see how this varies 
across colleges. Here's the question we want to get at -

Are there colleges whose students take a majority of their iCourses as required courses?

As with the previous question, we need to be clear on exactly how this is to be
interpreted. The college does __not__ represent the college to which the iCourse
belongs, but rather the college hosting the students' degree program. With that
in mind, we can say for example "of all the iCourses taken by students in a degree
program offered through the College of Liberal Arts and Sciences, 40% were taken
to complete a core degree requirement". Now on to the plot:
```{r}
data %>%
  filter(crse_modality == "ICOURSE",
         stud_modality == "F2F",
         !acad_prog %in% c("UGNFA", "UGPR", "UGTB", "UGUC")) %>%
  group_by(acad_prog) %>%
  summarise(prop_required = mean(required_course)) %>%
  ungroup() %>%
  ggplot(aes(reorder(acad_prog, -prop_required), prop_required)) + 
  geom_bar(stat = 'identity', fill = 'grey', color = 'black') +
  geom_text(aes(label = round(prop_required, 3)), vjust = -1, size = 3) +
  labs(x = "College",
       title = "Proportion of iCourses taken as core requirement") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank()) +
  ylim(0, 1)
ggsave("Graphics/prop_ico core.png")

```



Top 3:

* College of Nursing and Health Innovation (UGNU), 64.5%

* College of Public Service & Community Solutions (UGPP), 57.9%

* Mary Lou Fulton Teachers College (UGTE), 46.6%

Bottom 3:

* College of Liberal Arts and Sciences (UGLA), 21.1%

* College of Integrative Arts and Sciences (UGLS), 23%

* School for the Future of Innovation in Society (UGFI), 23.7%

There something very interesting that should be pointed out. First off, UGLS has the second
highest amount of ICO enrollments but the second lowest proportion of iCourses 
being taken as a core requirement. This would seem to suggest that students in 
these colleges are taking iCourses more often to fulfill elective/general studies
requirements. On the other hand, UGES (Engineering) has the lowest amount
of ICO enrollments but a little more than a third of those enrollments are for 
core courses - suggesting the opposite.


Now, let's see how this changes by degree program just as we did earlier. We want
to find out which degrees most/least often take iCourses for core credits. Note - 
we get rid of any degree programs with less than 1000 total course enrollments
over the entire time period.

```{r}
core_deg_props <- data %>%
  filter(acad_plan_type != c("NDG"),
         crse_modality == "ICOURSE",
         stud_modality == "F2F") %>%
  group_by(acad_plan) %>%
  summarise(prop_required = mean(required_course),
            count = n()) %>%
  filter(count >= 1000) %>%
  ungroup()

core_deg_props %>%
  top_n(10, prop_required) %>%
  ggplot(aes(reorder(acad_plan, -prop_required), prop_required)) + 
  geom_bar(stat = 'identity', color = 'black', fill = 'grey') +
  geom_text(aes(label = round(prop_required, 3)), vjust = -1, size = 3) +
  labs(x = "Degree",
       title = "Proportion of iCourses taken for core credit",
       subtitle = "(Top 10)") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1)) +
  ylim(0, 1)
ggsave("Graphics/top_ico_prop by deg.png")
```

Top 5:

* Community Health (NUCHLTBS), 72.5%

* Educational Studies (EDSLSTBAE), 67%

* Public Service and Public Policy - Emergency Management and Homeland Security (PPPAFEHBS), 66.1%

* Digital Culture - Music (HIDGCMBA), 64.7%

* Social Work (PPSWUSWU), 64.1%

```{r}

core_deg_props %>%
  top_n(10, -prop_required) %>%
  ggplot(aes(reorder(acad_plan, -prop_required), prop_required)) + 
  geom_bar(stat = 'identity', color = 'black', fill = 'grey') +
  geom_text(aes(label = round(prop_required, 3)), vjust = -1, size = 3) +
  labs(x = "Degree",
       title = "Proportion of iCourses taken for core credit",
       subtitle = "(Bottom 10)") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1)) +
  ylim(0, 0.25)
ggsave("Graphics/bttm_ico_prop by deg.png")
```

Bottom 5:

* Kinesiology (LAKINBS), 0.4%

* Business Administration (AGBUABS), 0.8%

* Exploratory Social and Behavioral Sciences (UCSBSEXPL), 1.1%

* Exploratory Humanities, Fine Arts, and Design (UCHUFAEXPLR), 1.2%

* Exploratory Health and Life Sciences (UCHSCIEXPL), 1.7%

There seems to be a pretty large difference between the top 10 and the bottom 10,
implying that students take iCourses for very different reasons across degree 
programs.


Finally, one last thing to check out - the distribution of the proportion of iCourses
taken for core credit. For each student, we will grab all of the iCourses that
they have ever taken and find the fraction of those courses that were required
courses. Once that's done for every tsudent, we can take a look at the distribution.
One note, though - there will likely be a lot of students who take very few iCourses.
The proportion that we calculate for these students may not be the best representation
of a students iCourse-taking habits. So for the sake of avoiding this problem,
we make the arbitrary decision to cut out students who have taken less than 10 
iCourses.

```{r}
core_props <- data %>%
  filter(acad_plan_type != c("NDG"),
         crse_modality == "ICOURSE",
         stud_modality == "F2F") %>%
  group_by(emplid) %>%
  summarise(prop_required = mean(required_course),
            count = n()) %>%
  filter(count >= 10) %>%
  ungroup()

ggplot(core_props) +
  stat_ecdf(aes(prop_required)) +
  xlim(0, 1) +
  labs(x = "Proportion",
       y = "Cumulative Density",
       title = "ECDF - Proportion of iCourses taken for Core Credit") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave("Graphics/ecdf_ico_core.png")
```
The ECDF gives us a basic idea of this distribution - sort of uniform and right-skewed.
Something to note from this graph is that 75% of students who have taken 10 or more iCourses
took less than half of them as required courses. In other words, a majority of the
students taking iCourses are taking them as electives.